### 2011-05-11 paper.tex
fixed silly typo

One of the technical details that will arise in many of our results is the need for polynomial time reductions. In this section, we will establish that all $\{\Sigma,\Pi,\bp,\parity\}$-constructible complexity classes are closed under polynomial time reductions. In particular, we need.

@@

\begin{theorem}\label{amplify}
Let $C$ be a \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class. Then \emph{$\bp \cdot C = \strongbp \cdot C$}.
\end{theorem}
Initially, this may seem to be obviously true for the same reasons that $\bp \cdot \p = \strongbp \cdot \bp$. The problem is that amplification requires running some machine which accepts a language in $C$ more than once. This requires the structure of $C$ to allow for such repetitions. This brings us to the concept of majority reductions.
\begin{definition}\label{defmajority}
We say that a complexity class $C$ is \emph{closed under majority reductions} if for any partial function $f \in C$, the partial function $\majority(f)$ defined by
$$\majority(f)(\langle x_1, \ldots, x_k\rangle) = 
\begin{cases}1 & \text{ if the number of $i$ such that }f(x_i) = 1\text{ is at least $\frac{k}{2}$} \\
0 & \text{ if the number of $i$ such that }f(x_i) = 0\text{ is at least $\frac{k}{2}$}\\
\x & \text{ otherwise}
\end{cases}$$
is in $C$.
\end{definition}
Now, we see that majority reductions are exactly what we want for amplification:
\begin{lemma}\label{majorityimpliesamplify}
If $C$ is a complexity class which is closed under majority reductions and polynomial time reductions, then\linebreak \emph{$\bp \cdot C = \strongbp \cdot C$.}
\end{lemma}
\begin{proof}
This is now the same application of the Chernoff bound which shows that $\bp \cdot \p = \strongbp \cdot \p$. Suppose $f$ is a partial function in $\bp \cdot C$. Then there is a partial function $g$ in $C$ such that $\pr_y [g(\langle x,y\rangle) = 1] > 2/3$ if $x\in L$ and $\pr_y [g(\langle x, y\rangle) = 0] > 2/3$ if $x\not\in L$, where the length of $y$ is equal to $p(|x|)$ for some polynomial $p$. Let $q$ be a polynomial, where $e^{-q(|x|)}$ is the desired error probability. Let $k = 48q(|x|)$.

@@

Hence, the sum will be odd if and only if $T$ accepts when the oracle calls are correct. Therefore, $L$ accepts $x$ if and only if this accepts for an odd number of choices of all the $a_i$, $b_i$, and $y_i$, and $L$ rejects $x$ otherwise. Thus, $L \in \parity \cdot C$. This is true for any $L \in \p^{\parity \cdot C}$, so $\p^{\parity \cdot C} \subseteq \parity \cdot C$.

\end{proof}
\begin{remark}\emph{
While this paper applies Theorem \ref{oracle} only in the case where $C$ is $\{\Sigma,\Pi,\bp,\parity\}$-constructible, it can also be used to show, for instance, that $\parity \cdot (\p^{\parity \cdot \pp}) = \parity \cdot \pp$, although it is nontrivial to show that $\pp$ is closed under intersection. For a proof, see \cite{Beigel}.
}\end{remark}

>>>>

One of the technical details that will arise in many of our results is the need for polynomial time reductions. In this section, we will establish that all $\{\Sigma,\Pi,\bp,\parity\}$-constructible complexity classes are closed under polynomial time reductions. In particular, we need

@@

\begin{theorem}\label{amplify}
Let $C$ be a \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class. Then \emph{$\bp \cdot C = \strongbp \cdot C$}.
\end{theorem}
Initially, this may seem to be obviously true for the same reasons that $\bp \cdot \p = \strongbp \cdot \bp$. The problem is that amplification requires running some machine which accepts a language in $C$ more than once. This requires the structure of $C$ to allow for such repetitions. This brings us to the concept of majority reductions.
\begin{definition}\label{defmajority}
We say that a complexity class $C$ is \emph{closed under majority reductions} if for any partial function $f \in C$, the partial function $\majority(f)$ defined by
$$\majority(f)(\langle x_1, \ldots, x_k\rangle) = 
\begin{cases}1 & \text{ if the number of $i$ such that }f(x_i) = 1\text{ is at least $\frac{k}{2}$} \\
0 & \text{ if the number of $i$ such that }f(x_i) = 0\text{ is at least $\frac{k}{2}$}\\
\x & \text{ otherwise}
\end{cases}$$
is in $C$.
\end{definition}
Now, we see that majority reductions are exactly what we want for amplification:
\begin{lemma}\label{majorityimpliesamplify}
If $C$ is a complexity class which is closed under majority reductions and polynomial time reductions, then \emph{$\bp \cdot C = \strongbp \cdot C$.}
\end{lemma}
\begin{proof}
This is now the same application of the Chernoff bound which shows that $\bp \cdot \p = \strongbp \cdot \p$. Suppose $f$ is a partial function in $\bp \cdot C$. Then there is a partial function $g$ in $C$ such that $\pr_y [g(\langle x,y\rangle) = 1] > 2/3$ if $x\in L$ and $\pr_y [g(\langle x, y\rangle) = 0] > 2/3$ if $x\not\in L$, where the length of $y$ is equal to $p(|x|)$ for some polynomial $p$. Let $q$ be a polynomial, where $e^{-q(|x|)}$ is the desired error probability. Let $k = 48q(|x|)$.

@@

Hence, the sum will be odd if and only if $T$ accepts when the oracle calls are correct. Therefore, $L$ accepts $x$ if and only if this accepts for an odd number of choices of all the $a_i$, $b_i$, and $y_i$, and $L$ rejects $x$ otherwise. Thus, $L \in \parity \cdot C$. This is true for any $L \in \p^{\parity \cdot C}$, so $\p^{\parity \cdot C} \subseteq \parity \cdot C$.
\end{proof}
\begin{remark}\emph{
While this paper applies Theorem \ref{oracle} only in the case where $C$ is $\{\Sigma,\Pi,\bp,\parity\}$-constructible, it can also be used to show, for instance, that $\parity \cdot (\p^{\parity \cdot \pp}) = \parity \cdot \pp$, although it is nontrivial to show that $\pp$ is closed under intersection. For a proof, see \cite{Beigel}.
}\end{remark}

We can use this remarkable fact to finish the proof of Lemma \ref{amplifymainlemma}, thus proving Theorem \ref{amplify}.
